An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-15 scagnostics.Rmd
More examples for bbh dataset.

```{r bbhGuided3, results="hide", fig.cap="Final views identified by the guided tour using the TIC index (left), the splines2d index (middle) or 1-convex (right)."}
bbhM3 <- rescale(select(bbhD, alpha, chi_tot, chi_p, ra, dec, distance))
if(!file.exists("cache/bbhGuidedSpline3.rda")){
  set.seed(2018)
  bbhTour23 <- save_history(bbhM3, guided_tour(splineIndex()))
  bbhTourFull23 <- as.list(interpolate(bbhTour23))
  save(bbhTour23, bbhTourFull23, file = "cache/bbhGuidedSpline3.rda")
} else {
  load("cache/bbhGuidedSpline3.rda")
}
iLast <- length(bbhTourFull23)
fProj2 <- bbhTourFull23[[iLast]]
dProj <- as.tibble(bbhM3 %*% fProj2)
p1 <- ggplot(dProj, aes(V1,V2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)
p2 <- ggplot(as.tibble(bbhM3), aes(ra, dec)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)
grid.arrange(p1, p2, ncol=2)
```

>>>>

```{r bbhGuided3, results="hide", fig.cap="Final views identified by the guided tour using the TIC index (left), the splines2d index (middle) or 1-convex (right)."}
bbhM3 <- rescale(select(bbhD, alpha, theta_jn, chi_tot, chi_p, ra, dec, distance))
getResWithSeed <- function(s){
  set.seed(s)
  startM <- orthonormalise(matrix(runif(14),ncol = 2))
  tourRes <- save_history(bbhM3, guided_tour(splineIndex()))
}

if(!file.exists("cache/bbhGuidedSpline3.rda")){
  set.seed(2018)
  seedVals <- sample(1:10000, 6)
  bbhRes1 <- getResWithSeed(seedVals[1])
  bbhRes2 <- getResWithSeed(seedVals[2])
  bbhRes3 <- getResWithSeed(seedVals[3])
  bbhRes4 <- getResWithSeed(seedVals[4])
  bbhRes5 <- getResWithSeed(seedVals[5])
  bbhRes6 <- getResWithSeed(seedVals[6])
  save(bbhRes1, bbhRes2, bbhRes3, bbhRes4, bbhRes5, bbhRes6, file = "cache/bbhGuidedSpline3.rda")
} else {
  load("cache/bbhGuidedSpline3.rda")
}
resList <- list(as.list(bbhRes1), as.list(bbhRes2), as.list(bbhRes3),
                as.list(bbhRes4), as.list(bbhRes5), as.list(bbhRes6))
pList <- list()
i <- 1
for (r in resList){
  iLast <- length(r)
  fProj <- r[[iLast]]
  dProj <- as.tibble(bbhM3 %*% fProj)
  pList[[i]] <- ggplot(dProj, aes(V1,V2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)
  i <- i+1
}
grid.arrange(pList[[1]], pList[[2]], pList[[3]],pList[[4]], pList[[5]], pList[[6]], ncol=3)
```

```{r constructedExample, results="hide", fig.cap="Selecting subset of 6 parameters, for which spline index can be used to improve constraint on parameter combination wrt ra vs dec."}
bbhC <- rescale(select(bbhD, m1, ra, chi_tot, alpha, distance, dec))
if(!file.exists("cache/constructedExample.rda")){
  set.seed(1999)
  tC <- save_history(bbhC, guided_tour(splineIndex()))
  save(tC, file = "cache/constructedExample.rda")
} else {
  load("cache/constructedExample.rda")
}
iL <- length(as.list(tC))
dProj <- bbhC %*% as.list(tC)[[iL]]
p1 <- ggplot(as.tibble(dProj), aes(V1, V2))+geom_point(alpha=0.02) + theme(aspect.ratio=1)
p2 <- ggplot(as.tibble(bbhC),aes(dec-alpha/5, ra)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)
p3 <- ggplot(as.tibble(bbhC),aes(dec, ra)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)
grid.arrange(p1, p2, p3, ncol=3)
```
